Towards Contract Modules for the Tezos Blockchain

### 2021-08-07 papers/contract-modules/fmbc2021/fmbc-main.tex
final version submitted

  Contract modules provide a statically checked interface to interact
  with contracts on the Tezos blockchain. A module specification
  provides all types as well as information about potential failure
  conditions of the contract. The specification is checked against the
  contract implementation using symbolic execution. An OCaml module is
  generated that contains a function for each entrypoint of the
  contract. The types of these functions fully describe the interface
  including the failure conditions and guarantee type-safe and
  sometimes fail-safe invocation of the contract on the blockchain.
\end{abstract}

@@

The contract modules approach does not provide a fixed API, but
rather generates a specific interface for each contract with one
function for each entrypoint of the contract. This
interface is statically checked against the contract implementation to
ensure type safety and exception safety. That is, values passed to an
interface function do not lead to type mismatches when invoking the
underlying contract. Morever, every failure condition arising during
contract execution is handled by proper error reporting according to
the interface.

@@

@@

As a concrete example, we consider a simple auction contract with the
header shown in Listing~\ref{lst:auction-header}. 
This contract has two entrypoints, \lstinline/close/ and \lstinline/bid/,
expressed by giving the single parameter a sum type. To call the
entrypoint \lstinline/close/ we invoke the contract with parameter \lstinline/Left ()/
otherwise we use \lstinline/Right ()/, where \lstinline/()/ is the sole
value of type \lstinline/unit/. The contract's storage is a nested pair which
contains a boolean flag and two addresses.

The contract works as follows. It is deployed with storage
\lstinline/(true,(owner,owner))/ which indicates that bidding is
allowed and the contract owner is currently the highest
bidder. On deployment the owner deposits an initial balance to indicate the
minimum bid. Closing the contract transfers the balance to the
owner. It is restricted to the owner. Closing as well as bidding fails
if the auction is
closed. If bidding is open and the amount of tokens accompanying the bid exceeds the
current highest bid, the current bidder replaces the previous highest
bidder and the previous highest bidder is reimbursed. Otherwise,
bidding fails, too.

To invoke this contract from an OCaml program, we generate an
OCaml module, say \lstinline/Auction/, from a specification of the
contract. This module contains two functions
\lstinline/close/ and \lstinline/bid/ corresponding to the
entrypoints. The type of these entrypoints reflects further properties
of these entrypoints as well as the ways in which an entrypoint might
fail.

@@

  entrypoint close ()
  raises "closed"               (** auction closed *)
       | "not owner"            (** caller cannot close *)
end
\end{lstlisting}
Listing~\ref{lst:contract-module-example} shows a contract module for
the auction contract.  It declares the entrypoint \lstinline/bid/ as
\lstinline/paid/, i.e., it should be invoked with a
non-zero amount of tokens, it states the pattern \lstinline/()/ for the
input value of type \lstinline/unit/, and it specifies two 
failure messages that we wish to deal with programmatically.
The \lstinline/close/ entrypoint is similar, but it is not
\lstinline/pair/. This contract reflects the understanding of the
programmer with the intention that the \lstinline/raises/ clauses
cover all failures that can arise during execution of the respective
entrypoint.

@@

  val close
    : Tezos.pukh -> ?fee:Tezos.mutez
    -> (Tezos.status, close_errors) Tezos.monad
\end{lstlisting}
% end 
Listing~\ref{lst:generated-signature} contains an OCaml module
signature as it would be generated from the contract module. The
module \lstinline/Tezos/ supposedly contains types and other low-level
Tezos-specific definitions. The type \lstinline/pukh/ for public
key hashes identifies contracts, the type \lstinline/mutez/ stands for
Tezos tokens, the type \lstinline/status/ reflects the internal return
status, and \lstinline/monad/ is an internal monad type. The signature
declares a function and an error type for each entrypoint.

The error types mirror the raises clauses. The first argument of each
function is the address of the contract, then an optional argument for
the transaction fee, an argument for passing an amount of tokens
(only for a paid entrypoint), the next argument would be for
the parameter; it is omitted here because its type is
\lstinline/unit/. The return type refers to the specific error type.

@@

We check the contract by symbolic execution against its
specification in the contract module. Symbolic execution proceeds in
the usual way by calculating a symbolic stack at each transition from
one Michelson instruction to the next. The initial stack is calculated
from the storage type, the parameter type, and the entrypoint.
As we aim to keep symbolic
values as concrete as possible, some instructions may turn out to be
unreachable or only reachable under certain conditions. This way, we
obtain, for each entrypoint, a set of final symbolic stacks along with
a path condition indicating when this final state is
reachable. Moreover, for each \lstinline/FAILWITH/ instruction we
obtain a symbolic value for the reported message and a path condition
indicating reachability of this instruction. We employ the SMT solver
Z3 \cite{DBLP:conf/tacas/MouraB08,DBLP:conf/setss/BjornerMNW18} to
check the feasibility of a path condition.

@@

For each entrypoint, we collect the set of reachable instructions.
For example, the  \lstinline/AMOUNT/ instruction obtains the amount of
tokens sent with a contract invocation.
It should not be possible to reach that instruction from an unpaid
entrypoint  like \lstinline/close/. This property is straightforward
to check from the path condition generated for the \lstinline/AMOUNT/
instruction.

For the \lstinline/FAILWITH/ instructions, we also collect their
arguments. The symbolic interpreter needs to retain concrete values as
much as possible to obtain precise results at this point. Each
argument to \lstinline/FAILWITH/ should be accounted for by one
\lstinline/raises/ clause.

For the simple auction contract the symbolic interpreter flags an
omission in the contract module
(Listing~\ref{lst:contract-module-example}). The problem is that
bidding returns the previous highest bid as part of the transaction
where the highest bidder is stored as a value of type
\lstinline/address/.  However, to receive a token transfer, this
address must by cast (by the Michelson implementation of the contract)
to an implicit contract of Michelson type \lstinline/(contract unit)/. This cast is unavoidable as a
value of contract type cannot be stored. However, the cast may fail and its failure leads to an
error condition that is reported with a \lstinline/FAILWITH/ instruction that is not covered by the
contract module.\footnote{We generated the Michelson code for this example using the Liquidity
  compiler (\url{https://www.liquidity-lang.org/}). While the failures for \lstinline/closed/ and
  \lstinline/too low/ are explicit in the source program, the compiler inserts the casts into the contract
  type automatically using the error message \texttt{No entrypoint default with parameter type
    unit}.}  The entrypoint for closing has the same issue with the address of the owner, who is
scheduled to receive the balance of the contract.

The best way to address this issue would be to assert that the addresses stored for the owner and
the highest bidder always cast successly into the \lstinline/(contract unit)/ type so that the
stated module type can be retained. Unfortunately, doing so requires control over the deployment of
the contract where the storage is initialized and it is not clear whether deployment should be part
of the API generated from a contract module.

The quick fix is to add \lstinline/raises/ clauses for the \texttt{No entrypoing \dots}
message. With this fix, we successfully check the module description against the Michelson
implementation of its contract.

\section{Advanced Checking}
\label{sec:advanced-checking}
\begin{lstlisting}[float,captionpos=b,caption={Enhanced contract module},label={lst:safer-contract-module}]
contract type SaferAuction = sig
  storage (Pair (bidding : bool) 
                (Pair (owner : address) (hi_bidder : address)))

  entrypoint close ()
  requires bidding raises "closed" (** auction closed*)
  ensures not bidding
  requires (sender = owner) raises "not owner"

  paid entrypoint bid () 
  requires bidding raises "closed" (** auction closed*)
  ensures bidding
  requires (amount > old.balance)
  raises "too low"                 (** bid too low *)
  ensures (balance >= old.balance)
  ensures (owner = old.owner)
end
\end{lstlisting}

As it is expensive to invoke a contract just to find out that it
fails, we propose to extend entrypoint specifications with
preconditions as shown in Listing~\ref{lst:safer-contract-module}. The
idea is that the generated OCaml module tries to check the
preconditions off-chain before invoking the contract. To this end, the
off-chain code needs to obtain properties like balance, storage etc of the
contract, but this information is available from a Tezos node without a fee! Of course, such an
off-chain check is prone to race conditions as concurrent contract invocations from other parties
may interfere and change the data before our module gets a chance to invoke the contract. 
We discuss two of the preconditions to highlight the properties that 
need to be analyzed and where race conditions may interfere.

The precondition \lstinline/sender = owner/ of \lstinline/close/ can
be checked off-chain because the owner's address is part of the
storage. However, it is in general unsound to perform such a test
off-chain because the owner's address could change if an entrypoint
changes that component of the storage. To safely check this
precondition, the analysis must determine that the owner component of
the storage remains the same across all possible execution paths of
the contract.

Moreover, the gathering of instructions must build path predicates,
such that each \lstinline/FAILWITH/ instruction comes with a predicate
that must be true to reach the instruction. In contract
implementation, the path predicate is \lstinline/sender != owner/. As
the conjunction of path predicate and precondition is unsatisfiable
and because the \lstinline/owner/ component is constant, an off-chain
test for \lstinline/sender = owner/ precisely predicts whether the
failure condition arises.

The situation is slightly more complex at the \lstinline/bid/
entrypoint. The failure \lstinline/"closed"/ is guarded by
\lstinline/bidding/. As the \lstinline/bidding/ component of the state can change,
precise prediction is not possible. A closer look reveals some
subtlety. If \lstinline/bidding/ is true, then the flag may have
changed by some interleaved call to \lstinline/close/. However, if
\lstinline/bidding/ is false, then there is no point in invoking the
contract because \lstinline/bidding/ will never be reset to true.

Hence the analysis should also record value transitions in the
storage for non-failing executions. For \lstinline/bidding/
\lstinline/bid/ transitions from true to true and \lstinline/close/
transitions from true to false. Thus, if the off-chain check finds
\lstinline/bidding/ $=$ false, then we can precisely predict that
\lstinline/bid/ would fail and trigger the corresponding error without
invoking the contract proper.

For the failure \lstinline/"to low"/, the analysis is very similar:
we need to know that there is no successful execution of
\lstinline/bid/ after an execution of \lstinline/close/. Moreover,
each invocation of \lstinline/bid/ raises the balance of the contract
monotonically. Thus, if the off-chain check
\lstinline/amount > balance/ fails, we can be sure that the contract
invocation will also fail; either because someone closed the auction or
because the balance is at least as high as in the off-chain sample. 
\section{Related work}
\label{sec:related-work}
%RPC APIs, often provided by current blockchains such as Ethereum \cite{eth-whitepaper} and Tezos \cite{tezos-whitepaper}, use loosely structured data, such as a JSON-based format, which is difficult for a programmatic program to handle. As a result, there is increasing work on providing better programmatic interfaces to the blockchains. Web3.js \cite{web3.js} provides an Ethereum JavaScript API and offers Java Script users a convenient interface to interact with the Etherum blockchain. Later, Web3.py \cite{web3.py}, derived from Web3.js, is developed to provide a Python library for interacting with Ethereum. Tezos prove a PRC API that utilizes JSON format for both input and output data, which is neither convenient nor programmatic.

@@

Status: the symbolic interpreter works on Michelson files which results from compiling the examples
provided with the Liquidity compiler. It generates human-readable output as well as output in the
SMTlib format suitable for SMT-solvers like Z3.

>>>>

  Contract modules provide a statically checked interface to interact
  with contracts on the Tezos blockchain. A module specification
  provides all types as well as information about potential failure
  conditions of the contract. The specification is checked against the
  contract implementation using symbolic execution. An OCaml module is
  generated that contains a function for each entry point of the
  contract. The types of these functions fully describe the interface
  including the failure conditions and guarantee type-safe and
  sometimes fail-safe invocation of the contract on the blockchain.
\end{abstract}

@@

The contract modules approach does not provide a fixed API, but
rather generates a specific interface for each contract with one
function for each entry point of the contract. This
interface is statically checked against the contract implementation to
ensure type safety and exception safety. That is, values passed to an
interface function do not lead to type mismatches when invoking the
underlying contract. Morever, every failure condition arising during
contract execution is handled by proper error reporting according to
the interface.

@@

A Michelson contract has a single default entry point. However, the \textit{parameter} type is
typically a sum type and each component of the sum can serve as a subsidiary entry point.

@@

As a concrete example, we consider a simple auction contract with the
header shown in Listing~\ref{lst:auction-header}. 
This contract has two entry points, \lstinline/close/ and \lstinline/bid/,
expressed by giving the single parameter a sum type. To call the
entry point \lstinline/close/ we invoke the contract with parameter \lstinline/Left ()/
otherwise we use \lstinline/Right ()/, where \lstinline/()/ is the sole
value of type \lstinline/unit/. The contract's storage is a nested pair which
contains a boolean flag and two addresses.

The contract works as follows. It is deployed with storage
\lstinline/(true,(owner,owner))/ which indicates that bidding is
allowed and the contract owner is currently the highest
bidder. On deployment the owner deposits an initial balance to indicate the
minimum bid. Closing the contract transfers the balance to the
owner. Closing is restricted to the owner. Closing as well as bidding fails
if the auction is
closed. If bidding is open and the amount of tokens accompanying the bid exceeds the
current highest bid, the current bidder replaces the previous highest
bidder and the previous highest bidder is reimbursed. Otherwise,
bidding fails.

To invoke this contract from an OCaml program, we generate an
OCaml module, say \lstinline/Auction/, from a specification of the
contract. This module contains two functions
\lstinline/close/ and \lstinline/bid/ corresponding to the
entry points. The type of these entry points reflects further properties
of these entry points as well as the ways in which an entry point might
fail.

@@

  entrypoint close ()
  raises "closed"               (** auction closed *)
       | "not owner"            (** caller cannot close *)
end
\end{lstlisting}
Listing~\ref{lst:contract-module-example} shows a contract module for
the auction contract.  It declares the entry point \lstinline/bid/ as
\lstinline/paid/, i.e., it should be invoked with a
non-zero amount of tokens, it states the pattern \lstinline/()/ for the
input value of type \lstinline/unit/, and it specifies two 
failure messages that we wish to deal with programmatically.
The \lstinline/close/ entry point is similar, but it is not
\lstinline/pair/. This contract reflects the understanding of the
programmer with the intention that the \lstinline/raises/ clauses
cover all failures that can arise during execution of the respective
entry point.

@@

  val close
    : Tezos.pukh -> ?fee:Tezos.mutez
    -> (Tezos.status, close_errors) Tezos.monad
\end{lstlisting}
% end 
Listing~\ref{lst:generated-signature} contains an OCaml module
signature as it would be generated from the contract module. The
module \lstinline/Tezos/ supposedly contains types and other low-level
Tezos-specific definitions. The type \lstinline/pukh/ for public
key hashes identifies contracts, the type \lstinline/mutez/ stands for
Tezos tokens, the type \lstinline/status/ reflects the internal return
status, and \lstinline/monad/ is an internal monad type. The signature
declares a function and an error type for each entry point.

The error types mirror the raises clauses. The first argument of each
function is the address of the contract, then an optional argument for
the transaction fee, an argument for passing an amount of tokens
(only for a paid entry point), the next argument would be for
the parameter; it is omitted here because its type is
\lstinline/unit/. The return type refers to the specific error type.

@@

We check the contract by symbolic execution against its
specification in the contract module. Symbolic execution proceeds by calculating a symbolic stack at
each transition from 
one Michelson instruction to the next. The symbolic interpreter is fully typed and rejects ill-typed
Michelson programs, if the ill-typed part is reachable from the default entry point. The initial
stack is calculated 
from the storage type, the parameter type, and the entry point.
As we aim to keep symbolic
values as concrete as possible, some instructions may turn out to be
unreachable or only reachable under certain conditions. This way, we
obtain, for each entry point, a set of final symbolic stacks along with
a path condition indicating when this final state is
reachable. Moreover, for each \lstinline/FAILWITH/ instruction we
obtain a symbolic value for the reported message and a path condition
indicating reachability of this instruction. We employ the SMT solver
Z3 \cite{DBLP:conf/tacas/MouraB08,DBLP:conf/setss/BjornerMNW18} to
check the feasibility of a path condition.

@@

For each entry point, we collect the set of reachable instructions.
For example, the  \lstinline/AMOUNT/ instruction obtains the amount of
tokens sent with a contract invocation.
It should not be possible to reach that instruction from an unpaid
entry point  like \lstinline/close/. This property is straightforward
to check from the path condition generated for the \lstinline/AMOUNT/
instruction.

For each entry point, we collect the set of reachable \lstinline/FAILWITH/ instructions along with
their path condition and their arguments. In most cases the symbolic interpreter finds a concrete
argument for each \lstinline/FAILWITH/ instruction because the typical usage pattern is to push a
concrete (string) value on the stack immediately preceding the \lstinline/FAILWITH/.
It remains to check that each argument to \lstinline/FAILWITH/ should be accounted for by one
\lstinline/raises/ clause.

Checking the simple auction contract in this way already flags an
omission in the contract module
(Listing~\ref{lst:contract-module-example}). The problem is that
bidding returns the previous highest bid as part of the transaction
where the highest bidder is stored as a value of type
\lstinline/address/.  However, to receive a token transfer, this
address must by cast (by the Michelson implementation of the contract)
to an implicit contract of Michelson type \lstinline/(contract unit)/. This cast is unavoidable as a
value of contract type cannot be stored. However, the cast may fail and its failure leads to an
error condition that is reported with a \lstinline/FAILWITH/ instruction that is not covered by the
contract module.\footnote{We generated the Michelson code for this example using the Liquidity
  compiler (\url{https://www.liquidity-lang.org/}). While the failures for \lstinline/closed/ and
  \lstinline/too low/ are explicit in the source program, the compiler inserts the casts into the contract
  type automatically using the error message \texttt{No entrypoint default with parameter type
    unit}.}  The entry point for closing has the same issue with the address of the owner, who is
scheduled to receive the balance of the contract.

The best way to address this issue would be to assert that the addresses stored for the owner and
the highest bidder always cast successly into the \lstinline/(contract unit)/ type so that the
stated module type can be retained. Unfortunately, doing so requires control over the initialization
of the storage, which is part of the deployment of the contract. At present, our design for contract
modules does not include support for the deployment of a contract. Moreover, it is not clear whether
it makes sense to support it as there is no guarantee
that a contract will be deployed using the API generated from a contract module.

The quick fix is to add \lstinline/raises/ clauses for the \texttt{No entrypoing \dots}
message. With this fix, we successfully check the module description against the Michelson
implementation of its contract. Another fix would be to rewrite the contract to enable the
dynamic creation of auctions.

\section{Advanced Checking}
\label{sec:advanced-checking}
\begin{lstlisting}[float,captionpos=b,caption={Enhanced contract module},label={lst:safer-contract-module},numbers=left]
contract type SaferAuction = sig
  storage (Pair (bidding : bool) 
                (Pair (owner : address) (hi_bidder : address)))

  entrypoint close ()
  requires bidding raises "closed"        (** auction closed*)
  requires (SOURCE = owner) raises "not owner"
  ensures not bidding
  ensures (post.BALANCE = 0)
  ensures (TRANSFER_TOKENS unit BALANCE hi_bidder)

  paid entrypoint bid () 
  requires bidding raises "closed"        (** auction closed*)
  requires (AMOUNT > pre.BALANCE) raises "too low" (** low bid *)
  ensures bidding 
  ensures (post.BALANCE = AMOUNT)
  ensures (post.hi_bidder = SOURCE)
  ensures (TRANSFER_TOKENS unit pre.BALANCE hi_bidder)

  invariant (post.owner = owner)
  invariant (post.bidding => bidding)
  invariant (post.hi_bidder = hi_bidder or post.hi_bidder = SOURCE)
end
\end{lstlisting}

As it is expensive to invoke a contract just to find out that it
fails, we propose to extend entry point specifications with
preconditions along with some global invariants as shown in Listing~\ref{lst:safer-contract-module}. The
idea is that the generated OCaml module tries to check the
preconditions off-chain before invoking the contract. To this end, the
off-chain code needs to obtain properties like balance, storage etc of the
contract, but this information is available from a Tezos node without a fee! Of course, such an
off-chain check is prone to race conditions as concurrent contract invocations from other parties
may interfere and change the data before our module gets a chance to invoke the contract.

Generally, a specification can refer to the values available to the contract. For example, the
instructions \lstinline/SOURCE/\footnote{The execution of a Michelson contract is part of
  a transaction, which can encompass several contract executions. The SOURCE of a Michelson contract
  is the originator of the entire transaction.}, \lstinline/BALANCE/, and \lstinline/AMOUNT/ refer
to the respective values. As the current \lstinline/BALANCE/ includes the \lstinline/AMOUNT/ sent
with the transaction, we write \lstinline/pre.BALANCE/ ($=$ \lstinline/BALANCE/ $-$
\lstinline/AMOUNT/) for the balance before the transaction starts and \lstinline/post.BALANCE/ for
the balance after the transaction finishes. The latter is calculated by subtracting the amounts
transferred from the current \lstinline/BALANCE/. The existence of a token transfer in the returned
operation list is indicated by
the respective \lstinline/TRANSFER_TOKENS/ instruction.  The components of the storage are referred
to by name. We distinguish the outgoing storage by prepending \lstinline/post./ as in
\lstinline/post.owner/.

For each clause \lstinline/requires/ $\Phi$ \lstinline/raises/ $s$, we take the path condition
$\Theta$ for a \lstinline/FAILWITH/ instruction with argument matching the string $s$ and check that
$\Phi \wedge \Theta$ is not satisfiable in the context given by the initial stack for the entry point.

From all \lstinline/requires/ $\Phi_i$ and \lstinline/ensures/ $\Psi_j$ clauses, we check that $\neg
(\bigwedge\Phi_i \to \bigwedge \Psi_j)$ is unsatisfiable in the context given by the initial stack
for the entry point and its corresponding final stack and path condition.

We discuss two of the preconditions to highlight the properties that 
need to be analyzed and where race conditions may interfere.

The precondition \lstinline/SOURCE = owner/ of \lstinline/close/ can
be checked off-chain because the owner's address is part of the
storage. However, it is in general unsound to perform such a test
off-chain because the owner's address could change if an entry point
changes that component of the storage. To safely check this
precondition, all other entry points must preserve the \lstinline/owner/'s address, which is indeed
the case by the postcondition in line~17. This postcondition is verified as outlined above.

% Moreover, the gathering of instructions must build path predicates,
% such that each \lstinline/FAILWITH/ instruction comes with a predicate
% that must be true to reach the instruction. In contract
% implementation, the path predicate is \lstinline/sender != owner/. As
% the conjunction of path predicate and precondition is unsatisfiable
% and because the \lstinline/owner/ component is constant, an off-chain
% test for \lstinline/sender = owner/ precisely predicts whether the
% failure condition arises.

The situation is slightly more complex at the \lstinline/bid/
entry point. The failure \lstinline/"closed"/ is guarded by
\lstinline/bidding/. As the \lstinline/bidding/ component of the state can change,
a precise prediction is not possible. A closer look reveals some
subtlety. If \lstinline/bidding/ is true, then the flag may have
changed by some interleaved call to \lstinline/close/. However, if
\lstinline/bidding/ is false, then there is no point in invoking the
contract because \lstinline/bidding/ will never be reset to true.
We address this situation by verifying the global invariant
\lstinline/post.bidding => bidding/.

For the failure \lstinline/"to low"/, the analysis is very similar:
we need to know that there is no successful execution of
\lstinline/bid/ after an execution of \lstinline/close/. Moreover,
each invocation of \lstinline/bid/ raises the balance of the contract
monotonically. Thus, if the off-chain check
\lstinline/AMOUNT > pre.BALANCE/ fails, we can be sure that the contract
invocation will also fail; either because someone closed the auction or
because the balance is at least as high as in the off-chain sample. Checking \lstinline/pre.BALANCE/
off-chain is particularly simple, because it is the current balance of the account.

\section{Symbolic interpretation of Michelson}
\label{sec:symb-interpr-mich}

Michelsym, our symbolic interpreter for Michelson, works in two stages. In the first stage, it
calculates symbolic stacks between each pair of reachable instructions. The underlying symbolic
domain comprises all concrete values, supports the type system, and generates a term representation
for symbolic values. Michelsym collects a path predicate that is extended at each conditional, but
which remains uninterpreted. If symbolic execution reaches certain instructions (most notably
\lstinline/FAILWITH/), Michelsym records the argument value and the path condition.

Presently, Michelsym works on Michelson files which result from compiling the examples
provided with the Liquidity compiler. It generates human-readable output as well as output in the
SMTlib format suitable for SMT-solvers like Z3. This output needs to be weaved together manually
with the formulas generated from a contract module.

We plan to revise Michelsym so that it directly communicates with Z3 to directly check for
unsatisfiable path conditions and to be better integrated with the contract module frontend.

\section{Related work}
\label{sec:related-work}
%RPC APIs, often provided by current blockchains such as Ethereum \cite{eth-whitepaper} and Tezos \cite{tezos-whitepaper}, use loosely structured data, such as a JSON-based format, which is difficult for a programmatic program to handle. As a result, there is increasing work on providing better programmatic interfaces to the blockchains. Web3.js \cite{web3.js} provides an Ethereum JavaScript API and offers Java Script users a convenient interface to interact with the Etherum blockchain. Later, Web3.py \cite{web3.py}, derived from Web3.js, is developed to provide a Python library for interacting with Ethereum. Tezos prove a PRC API that utilizes JSON format for both input and output data, which is neither convenient nor programmatic.

@@

### 2021-08-07 papers/contract-modules/fmbc2021/macros.tex
final version submitted

\lstset{
  language=Caml,
  basicstyle=\ttfamily,
  backgroundcolor=\color{pypypy},
  morekeywords={module,contract,sig,val,paid,entrypoint,raises},
  classoffset=1,
  morekeywords={nat,int,unit,string,or,pair,option,address,bool},
  morekeywords={Tezos,pukh,tz,status,monad},
  keywordstyle=\color{blue},
}

>>>>

\lstset{
  language=Caml,
  basicstyle=\ttfamily,
  backgroundcolor=\color{pypypy},
  morekeywords={requires,ensures,invariant,sender,amount,balance,storage,hash,module,contract,sig,val,paid,entrypoint,raises},
  classoffset=1,
  morekeywords={nat,int,unit,string,or,pair,option,address,bool},
  morekeywords={Tezos,pukh,mutez,status,monad},
  keywordstyle=\color{blue},
}
